A pipeline to analyse time-course gene expression data

### 2019-08-13 scripts/manuscript.Rmd
FIX disabling any installation through install_github
Travis keeps failing because of too many github API requests. From the
documentation, there's no way around doing github API requests. The fix
around rate limits is to provide a github key, which is going to be a
security breach once the repository is made public
Use new functionnality of moanin

```{r}
library(devtools)
install_github("NelleV/moanin", dependencies=FALSE)

@@

@@

- Why `dependicies=FALSE`? (same for the README for the repos). Seems easier to just say dependencies=TRUE and avoid the install.R routine. 
- I got an error in installation script for  packages:

@@

- `biocLite` is no longer the recommended way to install bioconductor. Instead
  `BiocManager::install(c("edge", "NMI"))`. But this is dependent on
  bioconductor/R version. Also, now that docker, can you change the
  installation to just be simple one-liner (and `BiocManager::install` can
  also do non-bioc packages, and is much more reliable.)

@@

```{r showMissingDEGenes, echo=FALSE}
exampleGenes<-names(signifCombos[signifCombos=="48,60,120,168"][1:10])
wh<-which(splines_model$meta$Group %in% c("K","M"))
plot_splines_data(data[exampleGenes,], splines_model, colors=ann_colors$Group)
```

**EAP: It would be nice to be able to subset in `plot_splines_data/plot_splines_data` to only some of the groups**

>>>>

```{r eval=FALSE}
library(devtools)
install_github("NelleV/moanin", dependencies)

@@

```{r echo=FALSE}
library(moanin)
```

@@

- I got an error in installation script for  packages:

@@

@@

```{r showMissingDEGenes, echo=FALSE}
exampleGenes<-names(signifCombos[signifCombos=="48,60,120,168"][1:10])
plot_splines_data(data, splines_model, subset_data=exampleGenes,
		  colors=ann_colors$Group)
```
